\documentclass{article}

% Packages required to support encoding
\usepackage{ucs}
\usepackage[utf8x]{inputenc}

% Packages required by code


% Packages always used
\usepackage{hyperref}
\usepackage{xspace}
\usepackage[usenames,dvipsnames]{color}
\hypersetup{colorlinks=true,urlcolor=blue}



\begin{document} 
\hypertarget{tutorial_4_step_by_step_example_heroku_sinatra_app}{}\subsection*{{Tutorial 4: Step by Step: Example Heroku Sinatra App}}\label{tutorial_4_step_by_step_example_heroku_sinatra_app}

TO-DO: show the steps required to create an integrated Salesforce/Heroku app which leverages OAuth web server flow and utilizes databasedotcom gem and Sinatra.

This section outlines the steps necessary to build a Hello World app that connects to database.com using the databasedotcom gem. We'{}ll use Sinatra as our web framework (because it'{}s lightweight) and Heroku as our deployment environment (because it rocks).

\hypertarget{heroku_setup}{}\subsection*{{Heroku setup}}\label{heroku_setup}

Complete the \textbf{\textbf{Prerequisites}} section of  if you haven'{}t already.

\hypertarget{stub_out_the_hello_world_app}{}\subsection*{{Stub out the Hello World app}}\label{stub_out_the_hello_world_app}

Create file \textbf{config.ru} with following contents:

Create file \textbf{Gemfile} with following contents:

\hypertarget{deploy_it}{}\subsection*{{Deploy it}}\label{deploy_it}

IMPORTANT: Note the name of your app; it will be referred to as \textbf{HEROKUAPP} in subsequent steps. In example above, the name of the app simple-robot-846.

\hypertarget{create_a_databasecom_account}{}\subsection*{{Create a database.com account}}\label{create_a_databasecom_account}

\begin{enumerate}%
\item Go to 
\item Click Signup
\item Fill in required fields (make note of username; will be referred to in subsequent steps as \textbf{USERNAME})
\item Click on link in the confirmation email you receive
\item Set a new password and submit (make note of password; will be referred to in subsequent steps as \textbf{PASSWORD})
\item Go to Personal Setup | My Personal Information | Reset My Security Token
\item Click button ``{}Reset Security Token''{}
\item Note the Security Token you receive via email; will be referred to in subsequent steps as \textbf{TOKEN}
\item Go to App Setup | Develop | Remote Access | New
\item Fill in the following: \textbf{Application}: Hello World \textbf{Callback}: https://\textbf{{HEROKUAPP}}.heroku.com/auth/salesforce/callback \textbf{Contact Email}: your email
\item Note Consumer Secret and Key in the Authentication section.

\end{enumerate}
\hypertarget{install_databasedotcom_and_sinatra_gems}{}\subsection*{{Install databasedotcom and Sinatra gems}}\label{install_databasedotcom_and_sinatra_gems}

1. $ git init Initialized empty Git repository in .git/ $ git add . $ git commit -m ``{}Hello world''{} Created initial commit 5df2d09: new app 44 files changed, 8393 insertions(+), 0 deletions(-)

\hypertarget{helloworld_improved_version}{}\subsection*{{``{}HelloWorld''{} Improved version}}\label{helloworld_improved_version}

You should see the following in your browser. 


\end{document}
